Untitled

### 2020-07-01 Thesis_Chapter_1/Supp_Material.tex
supp mat almost done

\hypertarget{supporting-information}{%
\section{Supporting information:}\label{supporting-information}}

\hypertarget{recipient-and-donor-characteristics-govern-the-hierarchical-structure-of-heterospecific-pollen-competition-networks}{%
\section{Recipient and donor characteristics govern the hierarchical
structure of heterospecific pollen competition
networks}\label{recipient-and-donor-characteristics-govern-the-hierarchical-structure-of-heterospecific-pollen-competition-networks}}

\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia Lynn Ashman,
Romina Rader

@@

\#TABLE S1 \begingroup\fontsize{7}{9}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\toprule
\textbf{Species} & \textbf{Common\_names} & \textbf{Variety} & \textbf{Source}\\
\midrule
\endfirsthead
\multicolumn{4}{@{}l}{\textit{(continued)}}\\
\toprule
Species & Common\_names & Variety & Source\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
\rowcolor{gray!6}  Brassica oleracea & Wild cabbage & Capitata & https://www.mrfothergills.com.au/\\
\addlinespace
Brassica rapa & Pak choi & Chinensis & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Eruca sativa & Rocket &  & https://www.mrfothergills.com.au/\\
\addlinespace
Sinapis alba & White mustard &  & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & Water spinach &  & https://www.theseedcollection.com.au/\\
\addlinespace
Ipomoea purpurea & Morning glory &  & http://www.shaman-australis.com.au\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & Capsicum & California Wonder & https://www.edenseeds.com.au\\
\addlinespace
Petunia integrifolia & Petunia &  & https://www.dianeseeds.com/\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersicum & Tomato & Tommy Toe & https://www.mrfothergills.com.au/\\
\addlinespace
Solanum melongena & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\*
\end{longtabu}
\endgroup{}

@@

TABLE S2
\begingroup\fontsize{6}{8}\selectfont

\resizebox{\linewidth}{!}{
\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{Species} & \textbf{Pollen size $\mu$m} & \textbf{Pollen grains per anther} & \textbf{Ovule number} & \textbf{Pollen:ovule ratio} & \textbf{Stigma area $\mu$m$^{2}$} & \textbf{Stigma length (mm)} & \textbf{Stigma width (mm)} & \textbf{Style length (mm)} & \textbf{Style width (mm)} & \textbf{Ovary length (mm)} & \textbf{Ovary width (mm)} & \textbf{Selfing rate} & \textbf{SI index}\\
\midrule
\rowcolor{gray!6}  Brassica oleracea & 27.72 & 42033 & 29 & 8696.48 & 0.62 & 0.53 & 0.88 & 2.32 & 0.65 & 5.93 & 1.11 & 0.0 & 0.00\\
\addlinespace
Brassica rapa & 25.35 & 7133 & 26 & 1646.08 & 0.36 & 0.37 & 0.73 & 1.08 & 0.52 & 3.53 & 0.88 & 0.0 & 0.00\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & 32.46 & 30761 & 241 & 765.83 & 1.06 & 0.72 & 1.18 & 3.24 & 1.06 & 3.15 & 5.80 & 0.8 & 0.64\\
\addlinespace
Eruca versicaria & 24.95 & 22151 & 24 & 5537.75 & 0.35 & 0.73 & 0.67 & 6.60 & 0.73 & 4.42 & 0.94 & 0.1 & 0.02\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & 70.10 & 858 & 4 & 1072.50 & 3.26 & 1.43 & 2.25 & 19.44 & 0.45 & 2.38 & 1.42 & 0.6 & 0.75\\
\addlinespace
Ipomoea purpurea & 97.59 & 654 & 6 & 545.00 & 2.27 & 1.24 & 1.88 & 28.23 & 0.58 & 1.06 & 1.57 & 1.0 & 2.74\\
\addlinespace
\rowcolor{gray!6}  Petunia integrifolia & 24.74 & 34657 & 220 & 787.66 & 1.17 & 0.80 & 1.32 & 14.65 & 0.45 & 3.13 & 1.77 & 0.9 & 0.26\\
\addlinespace
Sinapis alba & 33.59 & 3507 & 6 & 3507.00 & 0.55 & 0.63 & 0.91 & 3.62 & 0.77 & 1.98 & 1.07 & 0.7 & 1.12\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersicum & 22.00 & 28915 & 92 & 1885.76 & 0.09 & 0.19 & 0.35 & 6.47 & 0.31 & 1.16 & 1.13 & 0.7 & 0.48\\
\addlinespace
Solanum melongena & 25.18 & 166989 & 1010 & 992.01 & 1.14 & 0.96 & 1.33 & 11.33 & 0.94 & 4.02 & 3.55 & 1.0 & 1.45\\
\bottomrule
\end{tabu}}
\endgroup{}

@@

TABLE S3 \begingroup\fontsize{6}{8}\selectfont

\resizebox{\linewidth}{!}{
\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{Species} & \textbf{Hand cross-pollination} & \textbf{Hand self-pollination} & \textbf{Spontaneous selfing} & \textbf{Apomixis}\\
\midrule
\rowcolor{gray!6}  Brassica oleracea & 32.07 & 0.00 & 0.00 & 0\\
\addlinespace
Brassica rapa & 44.97 & 0.00 & 0.00 & 0\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & 80.00 & 56.47 & 19.34 & 0\\
\addlinespace
Eruca sativa & 23.75 & 0.42 & 0.00 & 0\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & 40.00 & 30.00 & 20.00 & 0\\
\addlinespace
Ipomoea purpurea & 31.67 & 86.67 & 31.67 & 0\\
\addlinespace
\rowcolor{gray!6}  Petunia integrifolia & 80.16 & 24.77 & 0.00 & 0\\
\addlinespace
Sinapis alba & 41.67 & 48.33 & 5.00 & 15\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersium & 85.65 & 41.20 & 68.48 & 0\\
\addlinespace
Solanum melongena & 60.48 & 74.87 & 21.56 & 0\\
\bottomrule
\end{tabu}}
\endgroup{}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{\textbf{Fig. S1} Average number of pollen grains per stigma for
20 different treatments (3 replicates per tratment). For each treatment,
we show the average number of conspecific pollen grains (grey) and
heterospecific pollen grains (light blue) per stigma. For each pair of
species on the x-axis, the first species is the recipient species, and
the second, the donor species.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{\textbf{Fig. S2} Average proportion of conspecific and
heterospecific pollen per stigma grouped by family, A) Brassicaceae, B)
Solanaceae and C) Convolvulaceae. These proportions (\%) are the number
of conspecific pollen grains or heterospecific pollen grains divided by
the total number of pollen grains per stigma for 20 different
treatments. We conducted 3 count replicates per treatment and then we
calculated the average number of pollen grains for these treatments. The
proportion of conspecific and heterospecific pollen are shown in grey
and light blue respectively. For each pair of species on the y-axis, the
first species is the pollen recipient and the second the pollen donor.
The vertical black line represents 50\% pollen of both donor and
recipient.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{\textbf{Fig. S3} Average proportion (\%) of heterospecific and
conspecific pollen per family for the different 20 treatments counted.
We conducted 3 count replicates per treatment and then we calculated the
average number of pollen grains for these different 20 treatments.
Finally, we grouped by family these treatments in order to see general
tendencies across families as pollen donor and as pollen recipient.
Pollen ratios were considered as the number of conspecific or
heterospecific pollen grains divided by the total number of pollen
grains per stigma. On the y-axis, the first family on each pair of plant
families is the recipient one, and the second, the family of the donor.
The vertical bar on intercept 50, represents equal proportions of both
recipient (grey) and donor (light blue) pollen.}
\end{figure}

>>>>

\section{Supporting information:}\label{supporting-information}

\section{Recipient and donor characteristics govern the hierarchical
structure of heterospecific pollen competition
networks}\label{recipient-and-donor-characteristics-govern-the-hierarchical-structure-of-heterospecific-pollen-competition-networks}

\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman,
Romina Rader

@@

\begingroup\fontsize{10}{12}\selectfont

\begin{longtabu} to \linewidth {>{\em}l>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\caption{\label{tab:unnamed-chunk-1}\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds.}\\
\toprule
\textbf{Species} & \textbf{Common names} & \textbf{Varieties} & \textbf{Source}\\
\midrule
\endfirsthead
\caption[]{\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds. \textit{(continued)}}\\
\toprule
Species & Common names & Varieties & Source\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
\rowcolor{gray!6}  Brassica oleracea & Wild cabbage & Capitata & https://www.mrfothergills.com.au/\\
\addlinespace
Brassica rapa & Pak choi & Chinensis & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Eruca sativa & Rocket &  & https://www.mrfothergills.com.au/\\
\addlinespace
Sinapis alba & White mustard &  & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & Water spinach &  & https://www.theseedcollection.com.au/\\
\addlinespace
Ipomoea purpurea & Morning glory &  & http://www.shaman-australis.com.au\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & Capsicum & California Wonder & https://www.edenseeds.com.au\\
\addlinespace
Petunia integrifolia & Petunia &  & https://www.dianeseeds.com/\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersicum & Tomato & Tommy Toe & https://www.mrfothergills.com.au/\\
\addlinespace
Solanum melongena & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\*
\end{longtabu}

\endgroup{}

@@

\begin{table}

\caption{\label{tab:unnamed-chunk-2}\textbf{Table S2.} Trait measurements ($\bar{X}$ ± SD) for the 13 different traits measured for each plant species. Detailed information of how pollen:ovule ratio, selfing rate and SI index were calculated is available in the plant functional traits section from the methods. }
\centering
\resizebox{\linewidth}{!}{
\fontsize{6}{8}\selectfont
\begin{tabu} to \linewidth {>{\em}l>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{Species} & \textbf{Pollen size $\mu$m} & \textbf{Pollen grains per anther} & \textbf{Ovule number} & \textbf{Pollen:ovule ratio} & \textbf{Stigma area $\mu$m$^{2}$} & \textbf{Stigma length (mm)} & \textbf{Stigma width (mm)} & \textbf{Style length (mm)} & \textbf{Style width (mm)} & \textbf{Ovary length (mm)} & \textbf{Ovary width (mm)} & \textbf{Selfing rate} & \textbf{SI index}\\
\midrule
\rowcolor{gray!6}  Brassica oleracea & 27.72 & 42033 & 29 & 8696.48 & 0.62 & 0.53 & 0.88 & 2.32 & 0.65 & 5.93 & 1.11 & 0.0 & 0.00\\
\addlinespace
Brassica rapa & 25.35 & 7133 & 26 & 1646.08 & 0.36 & 0.37 & 0.73 & 1.08 & 0.52 & 3.53 & 0.88 & 0.0 & 0.00\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & 32.46 & 30761 & 241 & 765.83 & 1.06 & 0.72 & 1.18 & 3.24 & 1.06 & 3.15 & 5.80 & 0.8 & 0.64\\
\addlinespace
Eruca versicaria & 24.95 & 22151 & 24 & 5537.75 & 0.35 & 0.73 & 0.67 & 6.60 & 0.73 & 4.42 & 0.94 & 0.1 & 0.02\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & 70.10 & 858 & 4 & 1072.50 & 3.26 & 1.43 & 2.25 & 19.44 & 0.45 & 2.38 & 1.42 & 0.6 & 0.75\\
\addlinespace
Ipomoea purpurea & 97.59 & 654 & 6 & 545.00 & 2.27 & 1.24 & 1.88 & 28.23 & 0.58 & 1.06 & 1.57 & 1.0 & 2.74\\
\addlinespace
\rowcolor{gray!6}  Petunia integrifolia & 24.74 & 34657 & 220 & 787.66 & 1.17 & 0.80 & 1.32 & 14.65 & 0.45 & 3.13 & 1.77 & 0.9 & 0.26\\
\addlinespace
Sinapis alba & 33.59 & 3507 & 6 & 3507.00 & 0.55 & 0.63 & 0.91 & 3.62 & 0.77 & 1.98 & 1.07 & 0.7 & 1.12\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersicum & 22.00 & 28915 & 92 & 1885.76 & 0.09 & 0.19 & 0.35 & 6.47 & 0.31 & 1.16 & 1.13 & 0.7 & 0.48\\
\addlinespace
Solanum melongena & 25.18 & 166989 & 1010 & 992.01 & 1.14 & 0.96 & 1.33 & 11.33 & 0.94 & 4.02 & 3.55 & 1.0 & 1.45\\
\bottomrule
\end{tabu}}
\end{table}

@@

\begin{table}

\caption{\label{tab:unnamed-chunk-3}\textbf{Table S3.} Results of the test of hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species. The values provided are the seed:ovule ratios in percentage.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{\em}l>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{Species} & \textbf{Hand cross-pollination} & \textbf{Hand self-pollination} & \textbf{Spontaneous selfing} & \textbf{Apomixis}\\
\midrule
\rowcolor{gray!6}  Brassica oleracea & 32.07 & 0.00 & 0.00 & 0\\
\addlinespace
Brassica rapa & 44.97 & 0.00 & 0.00 & 0\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & 80.00 & 56.47 & 19.34 & 0\\
\addlinespace
Eruca sativa & 23.75 & 0.42 & 0.00 & 0\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & 40.00 & 30.00 & 20.00 & 0\\
\addlinespace
Ipomoea purpurea & 31.67 & 86.67 & 31.67 & 0\\
\addlinespace
\rowcolor{gray!6}  Petunia integrifolia & 80.16 & 24.77 & 0.00 & 0\\
\addlinespace
Sinapis alba & 41.67 & 48.33 & 5.00 & 15\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersium & 85.65 & 41.20 & 68.48 & 0\\
\addlinespace
Solanum melongena & 60.48 & 74.87 & 21.56 & 0\\
\bottomrule
\end{tabu}}
\end{table}

@@

\begin{table}

\caption{\label{tab:unnamed-chunk-4}\textbf{Table S4.} Species x species matrix with the significance of effect “yes” or “no” of the different donors on seed set from the linear models. The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control. Significance was tested for all species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{6}{8}\selectfont
\begin{tabu} to \linewidth {>{\em}l>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright}X>{\raggedright}X}
\toprule
\em{} & \em{Brassica oleracea} & \em{Brassica rapa} & \em{Eruca sativa} & \em{Sinapis alba} & \em{Ipomoea aquatica} & \em{Ipomoea purpurea} & \em{Capsicum annuum} & \em{Petunia integrifolia} & \em{Solanum lycopersicum} & \em{Solanum melongena} & \em{$\%$ of significant effect}\\
\midrule
\rowcolor{gray!6}  B. oleracea &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 100\\
\addlinespace
B. rapa & No &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 88.9\\
\addlinespace
\rowcolor{gray!6}  E. sativa & Yes & No &  & No & Yes & No & No & No & No & No & 22.2\\
\addlinespace
S. alba & No & Yes & No &  & Yes & Yes & Yes & No & No & No & 44.4\\
\addlinespace
\rowcolor{gray!6}  I. aquatica & Yes & Yes & Yes & Yes &  & Yes & Yes & Yes & Yes & Yes & 100\\
\addlinespace
I. purpurea & No & No & Yes & No & No &  & Yes & No & Yes & No & 33.3\\
\addlinespace
\rowcolor{gray!6}  C. annuum & Yes & Yes & No & Yes & No & Yes &  & Yes & Yes1 & Yes & 77.8\\
\addlinespace
P. integrifolia & Yes & No & No & Yes & Yes & Yes & No &  & Yes & Yes & 67.7\\
\addlinespace
\rowcolor{gray!6}  S. lycopersicum & No & Yes & Yes & Yes & Yes & Yes & Yes & Yes &  & Yes & 88.9\\
\addlinespace
S. melongena & No & Yes & Yes & No & Yes & Yes & Yes & No & No &  & 55.6\\
\addlinespace
\rowcolor{gray!6}   &  &  &  &  &  &  &  &  &  &  & $\bar{X}=67.8$\\
\bottomrule
\end{tabu}}
\end{table}

@@

\begingroup\fontsize{7}{9}\selectfont

\begin{longtable}[t]{>{\em}lrrrr}
\caption{\label{tab:unnamed-chunk-5}\textbf{Table S5.} Results of the linear models conducted to test heterospecific pollen effect with the 50-50 CP-HP pollen treatments. We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept). The first species on the row names are the pollen recipient species and the second species the pollen donor species. Each treatment is compared with the control or reference treatment that is indicated with the recipient species names and the intercept term between parentheses}\\
\toprule
\textbf{ } & \textbf{Estimates} & \textbf{Standard error} & \textbf{t-value} & \textbf{{\textit{P}}-value}\\
\midrule
\rowcolor{gray!6}  M1 Petunia integrifolia - (Intercept) & 4.63 & 0.49 & 9.36 & 0.00\\
\addlinespace
M1 Petunia integrifolia - Brassica oleracea & -1.84 & 0.81 & -2.27 & 0.03\\
\addlinespace
\rowcolor{gray!6}  M1 Petunia integrifolia - Brassica rapa & -0.97 & 0.81 & -1.19 & 0.24\\
\addlinespace
M1 Petunia integrifolia - Capsicum annuum & 0.78 & 0.81 & 0.96 & 0.34\\
\addlinespace
\rowcolor{gray!6}  M1 Petunia integrifolia - Eruca vesicaria & -0.91 & 0.81 & -1.12 & 0.26\\
\addlinespace
M1 Petunia integrifolia - Ipomoea aquatica & -3.18 & 0.81 & -3.92 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M1 Petunia integrifolia - Ipomoea purpurea & -4.21 & 0.81 & -5.19 & 0.00\\
\addlinespace
M1 Petunia integrifolia - Sinapis alba & -2.99 & 0.81 & -3.69 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M1 Petunia integrifolia - Solanum lycopersicum & -2.40 & 0.81 & -2.96 & 0.00\\
\addlinespace
M1 Petunia integrifolia - Solanum melongena & -2.66 & 0.81 & -3.27 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M2 Solanum lycopersicum - (Intercept) & 4.39 & 0.24 & 18.54 & 0.00\\
\addlinespace
M2 Solanum lycopersicum - Brassica oleracea & -0.47 & 0.41 & -1.14 & 0.26\\
\addlinespace
\rowcolor{gray!6}  M2 Solanum lycopersicum - Brassica rapa & -2.74 & 0.41 & -6.67 & 0.00\\
\addlinespace
M2 Solanum lycopersicum - Capsicum annuum & -4.39 & 0.41 & -10.71 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M2 Solanum lycopersicum - Eruca vesicaria & -2.97 & 0.41 & -7.25 & 0.00\\
\addlinespace
M2 Solanum lycopersicum - Ipomoea aquatica & -4.13 & 0.41 & -10.06 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M2 Solanum lycopersicum - Ipomoea purpurea & -3.80 & 0.41 & -9.27 & 0.00\\
\addlinespace
M2 Solanum lycopersicum - Petunia integrifolia & -1.82 & 0.41 & -4.44 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M2 Solanum lycopersicum - Sinapis alba & -3.72 & 0.41 & -9.08 & 0.00\\
\addlinespace
M2 Solanum lycopersicum - Solanum melongena & -1.84 & 0.41 & -4.49 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M3 Solanum melongena - (Intercept) & 6.34 & 0.70 & 9.09 & 0.00\\
\addlinespace
M3 Solanum melongena - Brassica oleracea & -0.67 & 0.99 & -0.68 & 0.50\\
\addlinespace
\rowcolor{gray!6}  M3 Solanum melongena - Brassica rapa & -4.33 & 0.99 & -4.39 & 0.00\\
\addlinespace
M3 Solanum melongena - Capsicum annuum & -2.33 & 0.99 & -2.36 & 0.02\\
\addlinespace
\rowcolor{gray!6}  M3 Solanum melongena - Eruca vesicaria & -3.12 & 0.99 & -3.16 & 0.00\\
\addlinespace
M3 Solanum melongena - Ipomoea aquatica & -6.34 & 0.99 & -6.43 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M3 Solanum melongena - Ipomoea purpurea & -2.71 & 0.99 & -2.74 & 0.01\\
\addlinespace
M3 Solanum melongena - Petunia integrifolia & -1.43 & 0.99 & -1.45 & 0.15\\
\addlinespace
\rowcolor{gray!6}  M3 Solanum melongena - Sinapis alba & -1.11 & 0.99 & -1.12 & 0.26\\
\addlinespace
M3 Solanum melongena - Solanum lycopersicum & -0.84 & 0.99 & -0.86 & 0.39\\
\addlinespace
\rowcolor{gray!6}  M4 Capsicum annuum - (Intercept) & 4.59 & 0.52 & 8.78 & 0.00\\
\addlinespace
M4 Capsicum annuum - Brassica oleracea & -1.80 & 0.74 & -2.43 & 0.02\\
\addlinespace
\rowcolor{gray!6}  M4 Capsicum annuum - Brassica rapa & -2.51 & 0.74 & -3.39 & 0.00\\
\addlinespace
M4 Capsicum annuum - Eruca vesicaria & -0.63 & 0.74 & -0.85 & 0.40\\
\addlinespace
\rowcolor{gray!6}  M4 Capsicum annuum - Ipomoea aquatica & -1.36 & 0.74 & -1.84 & 0.07\\
\addlinespace
M4 Capsicum annuum - Ipomoea purpurea & -4.00 & 0.74 & -5.41 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M4 Capsicum annuum - Petunia integrifolia & -4.59 & 0.74 & -6.21 & 0.00\\
\addlinespace
M4 Capsicum annuum - Sinapis alba & -3.63 & 0.74 & -4.92 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M4 Capsicum annuum - Solanum lycopersicum & -1.52 & 0.74 & -2.06 & 0.04\\
\addlinespace
M4 Capsicum annuum - Solanum melongena & -3.29 & 0.74 & -4.46 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M5 Brassica oleracea - (Intercept) & 1.99 & 0.22 & 8.98 & 0.00\\
\addlinespace
M5 Brassica oleracea - Brassica rapa & -1.37 & 0.31 & -4.35 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M5 Brassica oleracea - Capsicum annuum & -0.87 & 0.31 & -2.76 & 0.01\\
\addlinespace
M5 Brassica oleracea - Eruca vesicaria & -1.92 & 0.31 & -6.13 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M5 Brassica oleracea - Ipomoea aquatica & -1.91 & 0.27 & -7.04 & 0.00\\
\addlinespace
M5 Brassica oleracea - Ipomoea purpurea & -1.99 & 0.31 & -6.35 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M5 Brassica oleracea - Petunia integrifolia & -1.64 & 0.31 & -5.21 & 0.00\\
\addlinespace
M5 Brassica oleracea - Sinapis alba & -1.57 & 0.31 & -4.99 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M5 Brassica oleracea - Solanum lycopersicum & -1.47 & 0.31 & -4.70 & 0.00\\
\addlinespace
M5 Brassica oleracea - Solanum melongena & -1.61 & 0.31 & -5.12 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M6 Brassica rapa - (Intercept) & 2.37 & 0.19 & 12.49 & 0.00\\
\addlinespace
M6 Brassica rapa - Brassica oleracea & -0.54 & 0.29 & -1.89 & 0.06\\
\addlinespace
\rowcolor{gray!6}  M6 Brassica rapa - Capsicum annuum & -1.42 & 0.29 & -4.94 & 0.00\\
\addlinespace
M6 Brassica rapa - Eruca vesicaria & -2.37 & 0.29 & -8.24 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M6 Brassica rapa - Ipomoea aquatica & -1.92 & 0.29 & -6.67 & 0.00\\
\addlinespace
M6 Brassica rapa - Ipomoea purpurea & -2.26 & 0.29 & -7.86 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M6 Brassica rapa - Petunia integrifolia & -2.37 & 0.29 & -8.24 & 0.00\\
\addlinespace
M6 Brassica rapa - Sinapis alba & -2.37 & 0.29 & -8.24 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M6 Brassica rapa - Solanum lycopersicum & -1.88 & 0.29 & -6.55 & 0.00\\
\addlinespace
M6 Brassica rapa - Solanum melongena & -2.37 & 0.29 & -8.24 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M8 Eruca sativa - (Intercept) & 1.34 & 0.35 & 3.80 & 0.00\\
\addlinespace
M8 Eruca sativa - Brassica oleracea & -1.34 & 0.50 & -2.69 & 0.01\\
\addlinespace
\rowcolor{gray!6}  M8 Eruca sativa - Brassica rapa & 0.66 & 0.50 & 1.32 & 0.19\\
\addlinespace
M8 Eruca sativa - Capsicum annuum & -0.27 & 0.50 & -0.55 & 0.58\\
\addlinespace
\rowcolor{gray!6}  M8 Eruca sativa - Ipomoea aquatica & 0.87 & 0.50 & 1.75 & 0.08\\
\addlinespace
M8 Eruca sativa - Ipomoea purpurea & -0.19 & 0.50 & -0.39 & 0.70\\
\addlinespace
\rowcolor{gray!6}  M8 Eruca sativa - Petunia integrifolia & 0.20 & 0.50 & 0.41 & 0.68\\
\addlinespace
M8 Eruca sativa - Sinapis alba & 0.32 & 0.50 & 0.65 & 0.52\\
\addlinespace
\rowcolor{gray!6}  M8 Eruca sativa - Solanum lycopersicum & -0.52 & 0.50 & -1.04 & 0.30\\
\addlinespace
M8 Eruca sativa - Solanum melongena & 0.54 & 0.50 & 1.09 & 0.28\\
\addlinespace
\rowcolor{gray!6}  M9 Ipomoea purpurea - (Intercept) & 0.82 & 0.20 & 4.05 & 0.00\\
\addlinespace
M9 Ipomoea purpurea - Brassica oleracea & 0.37 & 0.29 & 1.31 & 0.19\\
\addlinespace
\rowcolor{gray!6}  M9 Ipomoea purpurea - Brassica rapa & -0.41 & 0.29 & -1.43 & 0.16\\
\addlinespace
M9 Ipomoea purpurea - Capsicum annuum & -0.82 & 0.29 & -2.86 & 0.01\\
\addlinespace
\rowcolor{gray!6}  M9 Ipomoea purpurea - Eruca vesicaria & -0.75 & 0.29 & -2.62 & 0.01\\
\addlinespace
M9 Ipomoea purpurea - Ipomoea aquatica & 0.41 & 0.29 & 1.44 & 0.15\\
\addlinespace
\rowcolor{gray!6}  M9 Ipomoea purpurea - Petunia integrifolia & -0.37 & 0.29 & -1.31 & 0.19\\
\addlinespace
M9 Ipomoea purpurea - Sinapis alba & -0.33 & 0.29 & -1.14 & 0.26\\
\addlinespace
\rowcolor{gray!6}  M9 Ipomoea purpurea - Solanum lycopersicum & -0.82 & 0.29 & -2.86 & 0.01\\
\addlinespace
M9 Ipomoea purpurea - Solanum melongena & -0.24 & 0.29 & -0.82 & 0.41\\
\addlinespace
\rowcolor{gray!6}  M10 Ipomoea aquatica - (Intercept) & 0.80 & 0.09 & 9.36 & 0.00\\
\addlinespace
M10 Ipomoea aquatica - Brassica oleracea & -0.80 & 0.12 & -6.62 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M10 Ipomoea aquatica - Brassica rapa & -0.80 & 0.12 & -6.62 & 0.00\\
\addlinespace
M10 Ipomoea aquatica - Capsicum annuum & -0.80 & 0.12 & -6.62 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M10 Ipomoea aquatica - Eruca vesicaria & -0.80 & 0.12 & -6.62 & 0.00\\
\addlinespace
M10 Ipomoea aquatica - Ipomoea purpurea & -0.80 & 0.12 & -6.62 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M10 Ipomoea aquatica - Petunia integrifolia & -0.59 & 0.12 & -4.89 & 0.00\\
\addlinespace
M10 Ipomoea aquatica - Sinapis alba & -0.80 & 0.12 & -6.62 & 0.00\\
\addlinespace
\rowcolor{gray!6}  M10 Ipomoea aquatica - Solanum lycopersicum & -0.69 & 0.12 & -5.70 & 0.00\\
\addlinespace
M10 Ipomoea aquatica - Solanum melongena & -0.80 & 0.12 & -6.62 & 0.00\\
\bottomrule
\end{longtable}

\endgroup{}

@@

\begin{table}

### 2020-07-01 Untitled.Rmd
supp mat almost done

---
title: "Untitled"
output: html_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
setwd("~/R_projects/Hp_pollen_experiment")

@@

table<- data.frame(Correlation,Sum_squares, Significance,Trait,Family)
colnames(table) <- c("Correlation (r)","Sum of squares", "_P_-value", "Traits", "Family")
kable(table, format="markdown", digits = 2)
```

>>>>

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
  header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage[table]{xcolor}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage[normalem]{ulem}
---
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
setwd("~/R_projects/Hp_pollen_experiment")

@@

table<- data.frame(Correlation,Sum_squares, Significance,Trait,Family)
colnames(table) <- c("Correlation (r)","Sum of squares", "P-value", "Traits", "Family")

kable(table, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S8.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae and just Brassicaceae.") %>%
  kable_styling(latex_options = c("striped"), font_size = 7, full_width=F)%>% row_spec(0,bold=TRUE)

```
